---
title: "Croptimizer"
author: "Afton Coombs"
date: "1/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
This vignette provides an introduction to the `croptimizer` package
with a short walk through the functions use or a typical croptimizing
exercise.

## Crop data
Typically, you will start with the crop data stored in the package
as `croptimizer::crops`, although you are free to use your own data
so long as columns have the same names and data type.

```{r look-at-crops}
head(croptimizer::crops)
```

## Calculate base seed price
The first step is to calculate the cost of the seeds, which will depend on if you have a JojaMart membership or not. The `drop_cols`
parameter determines if intermediate columns used in calculating 
the base seed price should be preserved in the output or not. If you
would find these columns useful, then use `drop_cols = TRUE`.

```{r calc-seed-prices}
croptimized_data <-
  croptimizer::crops %>%
  calc_seed_prices(joja_member = FALSE, drop_cols = TRUE)
```

```{r calc-seed-prices-keeping-cols}
croptimized_data_with_extra_cols <-
  croptimizer::crops %>%
  calc_seed_prices(joja_member = FALSE, drop_cols = FALSE)
```

```{r diff-in-cols-from-drop-cols}
setdiff(colnames(croptimized_data_with_extra_cols),
        colnames(croptimized_data))
```

## Append the Soil Modification
Soil modifications are appended to introduce effects for fertilizers
and/or Speed-Gro. There are several ways to provide a `soil_mods` argument.

One way to provide the soil mod argument is via a singleton character. In this case, it will be replicated for the number of rows of the dataset.

```{r append-single-soil-mod}
croptimized_data <-
  croptimized_data %>%
  append_soil_mod(soil_mods = "Quality Fertilizer")
table(croptimized_data$soil_mod)
```

If no soil mod is supplied, then "Normal" is repeated for the number of rows of the data.
```{r append-no-soil-mod, options}
croptimized_data <-
  croptimized_data %>%
  append_soil_mod()
table(croptimized_data$soil_mod)
```

If an unnamed vector of appropriate length is provided, then it will be simply appended to the dataset.

```{r append-vector-soil-mod, options}
croptimized_data <-
  croptimized_data %>%
  append_soil_mod(soil_mods = c(rep("Quality Fertilizer", 18),
                                rep("Deluxe Fertilizer", 18)))
table(croptimized_data$soil_mod)
```

Finally, if a named vector of any length is provided, then it
will join to the crop data on those names, and any resulting NA's for soil mod will be filled with "Normal."

```{r append-named-soil-mod, options}
croptimized_data <-
  croptimized_data %>%
  append_soil_mod(soil_mods = c("Potato" = "Quality Fertilizer",
                                "Blueberry" = "Speed-Gro"))
table(croptimized_data$soil_mod)
```

## Filter to Seasons and Days
Next, we need to filter to crops that grow in this season, and crops
that have sufficient time to finish growing before the end of the season.
```{r filter_to_seasons_and_days}
croptimized_data <-
  croptimized_data %>%
  filter_to_season(season = "spring") %>%
  filter_to_days(day_of_season = 1)
```

## Calculate the Sale Price of the Crop
```{r calc-crop-sale-price}
croptimized_data <-
  croptimized_data %>%
  calc_crop_sale_price(farming_level = 5, level_5_tiller = TRUE)
```

## Calculate Net Profit
```{r add-net-profit}
croptimized_data <-
  croptimized_data %>%
  calc_net_profit()
```
